Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
shrink: smaller image

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=1\linewidth]{figures/episode_len_mean.pdf}
  \caption{Data collected during training. 
  We can see that two of the three neighbor-based strategies achieve performance similar to CTDE.
  }
  \label{fig:results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/scalability.pdf}
  \caption{ Communication overhead due to different neighboring strategies.
  }
  \label{fig:scalability}
\end{figure}

\section{Conclusion}\label{sec:conclusion}
This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE )with performance 
 comparable to centralized approaches (i.e., CTDE). 
%
These strategies offer the flexibility of DTDE while retaining the stability and performance of CTDE. 
%
Specifically, we introduce three approaches, namely: NN Averaging, NN Consensus and Experience Sharing
 which have been evaluated against various baselines, including CTDE, DTDE based on DQN, and MAPPO. 
%
The results show that two of the three proposed methods significantly enhance DTDE performance, achieving outcomes comparable 
 to CTDE, while NN consensus falls short of this goal, maintaining performance similar to DTDE. 
%
Furthermore, we analyzed the communication overhead, demonstrating that it remains minimal across all cases, 
 particularly with experience sharing, making it suitable for scenarios with very limited communication resources.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/episode_reward_mean.pdf}
  \includegraphics[width=0.8\linewidth]{figures/episode_len_mean.pdf}
  \caption{Data collected during training. 
  We can see that two of the three neighbor-based strategies achieve performance similar to CTDE.
  }
  \label{fig:results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/scalability.pdf}
  \caption{Communication overhead due to different neighboring strategies.
  }
  \label{fig:scalability}
\end{figure}

\section{Conclusion}\label{sec:conclusion}
This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE ) with performance 
 comparable to centralized approaches (i.e., CTDE). 
%
Specifically, we introduce three approaches, namely: K-NN averaging, K-NN consensus and experience sharing
 which have been evaluated against various baselines, including CTDE, DTDE based on DQN, and MAPPO. 
%
The results show that two of the three proposed methods significantly enhance DTDE performance, 
 achieving outcomes comparable to CTDE, 
 while NN consensus falls short of this goal,
  maintaining performance similar to DTDE. 
%
Furthermore, we analyzed the communication overhead, 
 demonstrating that it remains minimal across all cases, 
 particularly with experience sharing, 
 making it suitable for scenarios with very limited communication resources.
